{\large Gravitational wave sources in our Galactic backyard:}\\{\normalsize Predictions for BHBH, BHNS and NSNS binaries in LISA

### 2021-10-30 paper/tex/sections/variations.tex
add formation channel description
Updates from Overleaf

In this section we explore the effect of varying the underlying binary physics assumptions, both on the detection rate (Section~\ref{sec:detection_rate_analysis}) and the properties of the detectable systems (Section~\ref{sec:property_variations}).

\subsection{Detection rates}\label{sec:detection_rate_analysis}
In Figure~\ref{fig:detection_rates}, we show the expected number of LISA detections for each model variation and discuss the prominent trends in the following sections. For the exact rates and uncertainties plotted in this figure see Table~\ref{tab:detection_rates} and for a plot of the rates relative to the fiducial model see Fig.~\ref{fig:dco_relative_rates}.

The BHBH detection rate is markedly robust across variations of physics assumptions, as can be seen in the top panel of Figure~\ref{fig:detection_rates}, with the mean detections in three quarters of our models staying within 25\% of the fiducial rate. In contrast, the BHNS detection rate is very sensitive to all changes that we made in our binary physics assumptions, varying across two orders of magnitude in the middle panel of Figure~\ref{fig:detection_rates}. Finally, in the last panel of Figure~\ref{fig:detection_rates} we show that the NSNS detection is only moderately sensitive to certain changes in physics assumptions, varying by up to an order of magnitude, whilst showing no change for many models.

\subsubsection{Mass transfer variation trends}

In models \modBetaLow{}-\modBetaHigh{}, we set the mass transfer efficiency $\beta$ to a fixed value. For the BHBHs and BHNSs, as we increase $\beta$ the detection rates steadily decrease. This may seem unintuitive since one might assume that a higher mass transfer efficiency would lead to more massive compact objects and thus a more detectable population. However, this increase contributes to the envelope mass and so without increasing the core mass or fallback rate, the final compact object mass is relatively unaffected. Moreover, one must consider that most of these DCOs are formed through a common-envelope event and so retaining more of the envelope during mass transfer means that the eventual ejection of the envelope is much more difficult, thus leading to more stellar mergers and fewer detectable systems \citep[e.g.][]{Kruckow+2018,Broekgaarden+2021}.

In contrast, for the NSNSs, the detection rate increases with increasing $\beta$. This is for two main reasons: firstly the ejection of a common-envelope is less problematic for NSNSs as they are less massive \citep[e.g.][]{Kruckow+2018}. Moreover, the increased mass transfer efficiency means that systems that were previously below the mass necessary to become a NS can now accrete enough mass to form a NS. Although the same is true for more massive stars becoming BHs instead of NSs, due to the IMF, there is a net flux of more stars becoming NSs.

Enforcing that case BB mass transfer is always unstable (model \modCaseBB{}) has little effect on the BHBH detection rate whilst moderately and drastically decreasing the detection rates of BHNSs and NSNSs respectively. This is because a large fraction of NSs (and the majority of NSNS binaries) are formed through case BB mass transfer. Therefore, setting this mass transfer to be always unstable results in many of these binaries to merge before they could become DCOs since we assume the pessimistic common-envelope (CE) scenario by default.

If we instead use the optimistic CE scenario when setting case BB mass transfer to be unstable (model \modCaseBBOpt{}) we find that the rates instead uniformly increase across DCO types. This is both from the natural increases from using the optimistic CE scenario (see discussion of model \modOpt{} in Sec.~\ref{sec:detection_rate_CE_trends}), as well as additional increases from adding more DCOs formed through CE events after case BB mass transfer. This explains why we see more detections for BHNSs and NSNSs in model \modCaseBBOpt{} than in model \modOpt{}.

@@

\subsubsection{Common-envelope variation trends}\label{sec:detection_rate_CE_trends}

Models \modAlphaLowest{}-\modAlphaHighest{} alter $\alpha_{\rm CE}$, the common-envelope efficiency parameter, to $0.1, 0.5, 2.0$ and $10.0$ respectively (where the fiducial model has $\alpha_{\rm CE} = 1.0$). Although we see that there are large variations in the LISA detection rates when changing $\alpha_{\rm CE}$, the detectable \textit{fraction} of systems remains largely unchanged. Therefore, any changes in the detection rate are due to changes in the \textit{formation} rate of the DCOs.

Altering $\alpha_{\rm CE}$ has two major effects on the formation rate of double compact objects. Recall that $\alpha_{\rm CE}$ represents the fraction of the orbital energy that is available for the ejection of the common-envelope. Therefore, increasing $\alpha_{\rm CE}$ allows common-envelope ejection to occur at larger separations (since more energy is available at any given separation). A second effect of increasing $\alpha_{\rm CE}$ is that common-envelopes are less likely to result in stellar mergers as more energy is available for envelope ejection. We can understand the trends in formation rate of the three DCO types by considering these two effects.

The BHBH rate peaks for $\alpha_{\rm CE} = 1$ (model \modFid{}) and reduces whether we increase \textit{or} decrease $\alpha_{\rm CE}$. This is because the increase in $\alpha_{\rm CE}$ shifts a significant fraction of the population to such large separations that they no longer merge within a Hubble time. Although the number of stellar mergers decreases as well, the overall change in the merging BHBH formation rate is negative. The inverse is also true for decreasing $\alpha_{\rm CE}$, where BHBHs have shorter separations but stellar mergers are more frequent. Thus we find that $\alpha_{\rm CE} = 1$ seems to be optimal for BHBHs by balancing these two effects most effectively.

The BHNS rate follows the same pattern as BHBHs. This is expected since the BH is formed first for every BHNS in our sample and so the common-envelope event is due to a RLOF of BH progenitor, just as with BHBHs. However, given the similarity in the BHNS rates between $\alpha_{\rm CE} = 1$ and $\alpha_{\rm CE} = 2$ (models \modFid{} and \modAlphaHigh{}), the `optimal' $\alpha_{\rm CE}$ for BHNSs seems to be somewhere between 1 and 2 rather than very close to 1 as with BHBHs.

In contrast, $\alpha_{\rm CE} = 1$ is far from optimal for NSNSs. Increasing $\alpha_{\rm CE}$ (models \modAlphaHigh{} and \modAlphaHighest{}) results in significantly higher rates. This is because LISA detectable NSNSs tend to have been formed very recently before detection (see Fig.~\ref{fig:fiducial_pdf_distributions}e). Therefore, though higher $\alpha_{\rm CE}$ results in larger \textit{initial} separations, this does not adversely affect the NSNS rate as the systems are simply detected later after their formation compared to the fiducial model. So for models \modAlphaHigh{} and \modAlphaHighest{}, fewer systems result in stellar mergers and the overall population remains within the LISA band, producing much higher detection rates. %Finally, for model \modAlphaLowest{}, the reduction in common-envelope efficiency is strong enough that a sufficient number of systems are formed at shorter separations to offset those lost to stellar mergers.

We explore the optimistic CE scenario in model \modOpt{}, meaning that we allow Hertzsprung gap donors to survive CE events. A large fraction of the progenitors of the BHs in our sample expand significantly during the Hertzsprung gap phase and initiate CE events. This means that, when we assume the optimistic CE scenario, the formation rate of BHs is greatly increased. Therefore, similar to models \modAlphaLowest{}-\modAlphaHighest{}, we find that though the detectable \textit{fraction} does not change significantly, the increased formation rate of BHs in the Milky Way leads to this model predicting significantly more BHBH detections.

The progenitors of BHNSs tend to be less massive than those of BHBHs. Less massive stars expand less during the Hertzsprung gap and thus initiate CE events less frequently in this phase. For these reasons, as can be seen most clearly in Fig.~\ref{fig:dco_relative_rates}, the relative increase in model \modOpt{} compared to the fiducial model is lower than BHBHs for BHNSs. For the same reason, the NSNS detection rate shows little significant change.

\subsubsection{Supernova variation trends}

Changes to the remnant mass prescription (models \modRapid{}-\modNSHigh{}) have no effect on the NSNS detection rate for two reasons. A large fraction of the NSs in our sample are formed through ECSN, in which case their masses are set to $1.26 \unit{M_\odot}$ regardless of the remnant mass prescription. Secondly, the majority of the remaining NSs have such low progenitor masses that they are set to the lowest remnant mass in the prescription ($1.28 \unit{M_\odot}$ for the delayed prescription and $1.1 \unit{M_\odot}$ for the rapid prescription). This means that changing the upper portion of the mass range of NSs in the remnant mass prescription has little effect.

This is not the case for BHBHs and BHNSs. The different remnant mass prescriptions and maximum neutron star masses change whether a progenitor becomes a black hole or a neutron star. Hence, using the rapid prescription (model \modRapid{}) or increasing the maximum neutron star mass (model \modNSHigh{}), means that more progenitors form high mass NSs rather than low mass BHs and so more BHNSs are formed. This explains the higher detection rates for BHNSs and lower detection rates for BHBHs in these models. The inverse is true for model \modNSLow{}, where instead more BHBHs are formed and detected.

Additionally, we find that not implementing pair-instability supernovae (PISN) pulsational pair-instability supernovae (PPISN) in model \modNoPISN{} has no effect on the results for any DCO type. This is because the average metallicity of the Milky Way is high enough than no progenitor retains enough mass to initiate a PISN or PPISN.

Decreasing the core-collapse supernova velocity dispersion (models \modSigLow{}-\modSigLower{}) increases the detection rates for each DCO type since lower kicks result in fewer disrupted binaries and hence a more numerous detectable population. This increase is least prominent for BHBHs since their increased mass mean that disruptions are less frequent than, for instance, in NSNSs. It is also notable that these two models best match the detection rates from LIGO (Broekgaarden et al.\ in prep). Therefore we find the best matching models for the LIGO detection rates also produce the highest LISA detection rates.

In model \modNoBH{} we do not give black holes natal kicks. For BHBHs, the rate is approximately equal to that of model \modSigLower{} since kicks of $30 \unit{km}{s^{-1}}$ are equivalent to no kicks for massive BHs in our sample. For BHNSs, this model's rate is still well above the fiducial but decreases slightly relative to model \modSigLower{} as the number of surviving binaries is limited by the neutron star kick more than the black hole kick. NSNSs are unaffected as one would assume due to the absence of BHs.

\subsubsection{Stellar wind variation trends}
We decrease the efficiency of Wolf-Rayet winds to 10\% in model \modWRLow{}. We find that decreasing the efficiency of these winds actually has very little effect on our predicted detection rates. This due to a combination of cancelling effects.

Firstly, the decreased winds mean that the DCOs (particularly those containing BHs) are generally more massive and so more detectable in LISA. Secondly, one may expect that LISA sources in model \modWRLow{} would be higher frequency than in our fiducial model as decreased winds generally result in tighter binaries. However, though this \textit{is} the case at DCO formation, we find by the time the sources have evolved until the LISA mission they are actually at \textit{lower} frequencies than in our fiducial model. This is because the reduced winds allow DCOs to be formed at higher metallicity and, therefore, at more recent times. This means that the DCOs do not evolve for as long before the LISA mission and so remain at lower frequencies (wider separations) thus making them less detectable. Finally, we find that NSNSs are more eccentric and BHBHs are less eccentric than our fiducial model (with BHNSs relatively unchanged). The increase in eccentricity for NSNSs comes from the same reason as the lower frequency, more recent birth times mean that binaries have less time to circularise. The same is not true for BHBHs as the more massive systems are less affected by supernova kicks and so fewer high eccentricity systems are formed.

Overall, despite the large differences in the system properties, these three effects in combination leave the detection rates relatively unchanged.

In model \modWRHigh{} we instead \textit{increase} the efficiency of Wolf-Rayet winds by a factor of 5. In this model the detection rate of BHBHs decreases by over a factor of 10 and BHNSs by over a factor of 2 whilst the NSNS rate is relatively unchanged. Increasing the efficiency of WR winds strongly decreases the final masses of DCOs. This means that many progenitors that would have formed LISA sources under our fiducial assumptions would not have enough mass to produce a DCO, or produce a NS instead of a BH (therefore this effect is stronger on BHBHs than NSNSs). Moreover, DCOs that are formed tend to be less massive and therefore less detectable.

@@

\subsubsection{Effect of mass loss efficiency on mass distribution}

\begin{figure}[tb]
    \centering
    \includegraphics[width=\columnwidth]{fig12_wr_wind_mass_variations.pdf}
    \caption{As Fig.~\ref{fig:lower_mass_gap_variation}, but instead varying Wolf-Rayet wind efficiency (models \modWRLow{} and \modWRHigh{}). \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig12_wr_wind_mass_variations.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/variations.ipynb}{\faBook}.}
    \label{fig:wr_wind_mass_variations}
\end{figure}

>>>>

In this section we explore the effect of varying the uncertain assumptions governing the evolution of binary system and the formation of compact objects. For this we use the model variations presented in \citet{Broekgaarden+2021}.

We first discuss the robustness of our predictions for the number of detectable systems (Section~\ref{sec:detection_rate_analysis}). We then discuss examples of how the observable properties of the detectable systems, such as the distribution of masses and eccentricities, are affected and can potentially be used to probe about the physics of double compact object formation (Section~\ref{sec:property_variations}).

%We note that impact of physics variations cannot always be easily understood in simple terms as the evolutionary path of a progenitor of a detectable source involves multiple interactions stages. Providing full explanations is beyond our current scope, but we hope nevertheless that this section gives the reader an impression of the impact of the physics variations on the rates.

\subsection{Detection rates}\label{sec:detection_rate_analysis}
In Figure~\ref{fig:detection_rates}, we show the number of LISA detections as predicted by our simulations considering variations in the physical assumptions.  We show predictions for  BHBH, BHNS and NSNS systems in the top, middle and bottom panel respectively. All the rates and their uncertainties plotted in this figure are also provided in Table~\ref{tab:detection_rates}. 
In the sections that follow, we briefly explain the variations considered and discuss the most prominent trends.

\subsubsection{Efficiency of mass transfer}

The efficiency of mass transfer, i.e.\ the fraction of mass lost by the donor through Roche lobe overflow that is accreted by the companion, is poorly constrained and is considered as one of the main uncertainties in binary evolution \citep[e.g.\ ][]{deMink+2007}. In our fiducial model A, we use a prescription where the 
accretion rate onto stellar companions is regulated by their thermal timescale, i.e. the timescale on which a star can react to changes and restore thermal equilibrium \citep[see e.g.\ ][]{Schneider+2015}.

In models \modBetaLow{}-\modBetaHigh{}, we adopt a fixed value for the mass transfer efficiency, $\beta$, from $\beta=0.25$ up to 0.75, in cases of stable mass transfer onto a stellar companion. For accretion onto NS and BH we still assume that their accretion is limited to the Eddington rate.

Nearly all systems that can be detected form through channels where the very first interaction is stable mass transfer. Generally, higher mass transfer efficiencies lead to higher masses for the accreting stars, but also leads to wider orbits \citep{Soberman+1997, vanSon+2020}. 
Changing $\beta$ thus already affects the masses and orbital separation after the first interaction phase, which in turn changes the starting conditions and outcome of all subsequent interactions phases. This makes it complicated to fully understand the impact of varying $\beta$ in simple terms, but we can distinguish two main patterns for higher and lower mass systems respectively.

For the most massive progenitors, increasing $\beta$ leads to secondary stars that are so massive and luminous that they experience strong wind mass loss. This leads to further widening of the orbit and it limits the amount by which the secondaries expand. Both of these effects can prevent secondaries from filling their Roche lobe. This means that they cannot initiate the reverse interaction needed to shrink the binary system and eventually produce a detectable compact binary system. We indeed see that increasing the mass transfer efficiency leads to 
a decrease of the expected number of detections for BHBHs and BHNSs, which originate from the most massive progenitors.

For lower mass progenitors, which primarily produce NSNS systems, we find the opposite. Increasing $\beta$ leads to an increase of detectable systems. This is in part because the increased mass of the secondary stars allows stars that would have other wise ended their life as a WD, can now become massive enough to form a NS. The same effect also allows some NS progenitors to become massive enough to BH progenitors, but this effect is less strong. Furthermore, the changes in secondary mass and orbital widening, affects the number of systems for which the reverse interaction successfully ejects the envelope and shrinks the orbit. Indeed, the net effect is an increase of NSNS systems with increasing $\beta$.

@@

\subsubsection{Common-envelope evolution}\label{sec:detection_rate_CE_trends}

The common-envelope phase constitutes the most challenging phase in the evolution of interacting binary systems \citep{Ivanova+2013}. The debate concerns the conditions required for the onset of a common envelope phase and, if a common envelope phase occurs, what the outcome is. Rapid populations synthesis simulations such as ours approximate both questions in a crude way. We therefore consider several model variations.

\paragraph{The efficiency parameter $\alpha_{\rm CE}$} To estimate the outcome of a CE phase, we use a simple consideration of the binding energy and orbital energy  \citep{Webbink+1984}. Our fiducial model assumes a common-envelope efficiency parameter $\alpha_{\rm CE} = 1$ which can be interpreted as the case where all the energy liberated by shrinking the orbit it used in an optimal way to unbind the envelope \citep{Webbink+1984}. There have been many attempts to constrain this parameter using observations and more recently also using 3D simulations, but no consistent picture has emerged. Therefore we consider variations in this parameter.

In models \modAlphaLowest{}-\modAlphaHighest{} we alter the common-envelope efficiency parameter $\alpha_{\rm CE}$ to $0.1, 0.5, 2.0$ and $10.0$ respectively. Values smaller than 1 may represent cases where not all energy is used efficiently to unbind the envelope, for example when part of the energy escapes in the form of radiation or if part is used to impart additional kinetic energy in the ejecta. Values larger than 1 may represent cases where additional energy sources can be tapped into, such as for example jets powered by accretion. The variations can also be seen as a way to cover uncertainties in estimates for the binding energy itself.

Increasing $\alpha_{\rm CE}$ makes common-envelope ejection more efficient or, in other words, less orbital shrinkage is needed to successfully eject the envelope. This has two consequences. (1) Firstly, a larger fraction of systems avoids merging during the CE phase. This increases the overall number of double compact object binaries. (2) Secondly, the systems that survive the CE phase are wider, possibly too wide to become detectable as gravitational wave sources. So, while the first consequence favours the formation of double compact object systems, the second consequence disfavours the subset of those close enough to be detected.

These two opposing effect result in fine tuning situation. Only a very small subset of progenitor systems that have the right orbital parameters prior to the CE phase to successfully produce detectable systems. Changing  $\alpha_{\rm CE}$ moves and changes this window in the parameter space that successfully leads to the formation of detectable systems. How the number of the detectable systems changes depends on whether the relevant parameter space grows or shrinks and on how well the relevant part of the parameters space is populated. Fully unravelling these effects and how they interplay with the assumed star formation history is beyond our scope (and possibly not even of large relevance given the severe simplifications). We will limit the further discussions to simply stating the trends we observe.

We find that the BHBH rate peaks for $\alpha_{\rm CE} = 1$ (model \modFid{}) and reduces whether we increase \textit{or} decrease $\alpha_{\rm CE}$. The BHNS rate follows the same pattern as BHBHs although the value of $\alpha_{\rm CE}$ which maximises BHNSs seems to be between 1 and 2. In contrast, for NSNSs we find that increasing $\alpha_{\rm CE}$ (models \modAlphaHigh{} and \modAlphaHighest{}) results in significantly higher rates.

\paragraph{The ``optimistic'' CE treatment} We further explore a model variation introduced by \citet{Belczynski+2007} often referred to as the ``optimistic'' CE scenario. This model also considers donor stars that are on the Hertzsprung as the progenitors for CE events.

In agreement with other studies, we find that this treatment leads to a large increase formation rate of BHBHs and with it the number of systems that LISA can detect. This is because BHBHs originate from the most massive progenitors, which in expand very significantly during the Hertzsprung gap phase in our simulations. The progenitors are likely initiate interaction during this phase. Our predictions for the number of detectable systems increases by a factor 2. The less massive progenitors of BHNSs are less strongly affected, and for NSNS we do not see a significant increase.

\paragraph{Case BB mass transfer} For completeness and consistency with \citet{Broekgaarden+2021}, we have also included model variations that consider uncertainties in case BB mass transfer. his is a phase of mass transfer where the donor star has already lost its hydrogen envelope in a prior interaction, but fills its Roche lobe again as expands during helium shell burning phase \citep[e.g.][]{Dewi+2003, Vigna-Gomez+2018}. This is of particular interest for the formation of NS stars, as their lower mass progenitors are swelling the most during this phase \citet[e.g.][and references therein]{Laplace+2020}. Nearly all NSNS systems from through case BB mass transfer

In model \modCaseBB{} we effectively exclude any systems that evolve through case BB mass transfer. As expected, this kills nearly all NSNS systems. We also find a heavy reduction of the BHNS systems y a factor 6. The BHBH systems are not affected, as expected, since case BB mass transfer does not play a role for high mass progenitors.

Finally, in model {[\bf TOM.. please add label]} [=F] we consider a situation where case BB mass transfer always leads to unstable mass transfer and initiates a CE phase combined with the optimistic treatment for CE. This model leads to the highest predictions for the detection's among all variations that we have considered.

\subsubsection{Supernovae and compact remnants}

The formation of compact remnants and and their associated natal kicks also constitute important uncertainties.

In model \modRapid{} we consider the so-called ``rapid'' remnant mass function by \citet{Fryer+2015} as an alternative to the ``delayed'' description used in our detailed simulations. This affects the mass distribution (see Section~\ref{XX}), but the effects on the number of detectable systems is modest for BHBH and BHNS, and negligible for NSNS.

The same is true for changing the impact of changing the assumed maximum neutron star mass, $m_{\rm ns}$ (\modNSLow{} and \modNSHigh{}). Lowering $m_{\rm ns}$  increases the number of detections involving BHs and vice versa, but has no significant effect on the number of NSNS detections.

In Model \modNoPISN{}, we ignore pair instability supernovae, which has no significant effect on the predictions for the number of detections with LISA. This is not a surprise as the typical metallicity of the progenitors in our Milky Way is rather high.  The detectable systems are dominated by systems with final core masses that are well below the mass regime for pair instability supernovae.

Decreasing the natal kicks for all core-collapse supernovae (models \modSigLow{}-\modSigLower{}) increases the detection rates for each DCO type since lower kicks result in fewer disrupted binaries and hence a more numerous detectable population. The NSNS systems are most strongly affected.   The impact on BHNS systems is mild and even insignificant for BHBH systems. This is because, in our models, the natal kicks for BHs are scaled down with the amount of mass that falls back, which is large in the case of BHs.

In model \modNoBH{} we assume BHs form without any kick, while using our fiducial assumption for the natal kicks of neutron stars.  This increases the predictions for BHNS by a factor 3. The impact on BHBH systems is much smaller, This is because they mostly form from more massive cores which are already assumed to form with low kicks in our simulations.  As expected, the NSNS population is not affected.

%We note that the these two models best match the detection rates from LIGO (Broekgaarden et al.\ subm). Therefore we find the best matching models for the LIGO detection rates also produce the highest LISA detection rates.

\subsubsection{Stellar winds}
Mass loss in the form of stellar winds or eruptions are also a main incertainty. It affects by how much stars can grow in size and it affects the final core masses.

\citet{Broekgaarden+2021} provides us with model variations that consider variations in the mass loss by hot and luminous Wolf-Rayet stars.   We find that a reduction of the wind mass loss  has very little effect on our predictions.  It turns out that this is the consequence of several effects that cancel each other.

Firstly, the decreased winds mean that the DCOs (particularly those containing BHs) are generally more massive and so more detectable in LISA. Secondly, one may expect that LISA sources in model \modWRLow{} would be higher frequency than in our fiducial model as decreased winds generally result in tighter binaries. However, though this is the case at DCO formation, we find by the time the sources have evolved until the LISA mission they are actually at lower frequencies than in our fiducial model. This is because the reduced winds allow DCOs to be formed at higher metallicity and, therefore, at more recent times. This means that the DCOs do not evolve for as long before the LISA mission and so remain at lower frequencies (wider separations) thus making them less detectable.

In addition, we find that NSNSs are more eccentric and BHBHs are less eccentric than our fiducial model (with BHNSs relatively unchanged). The increase in eccentricity for NSNSs comes from the same reason as the lower frequency, more recent birth times mean that binaries have less time to circularise. The same is not true for BHBHs as the more massive systems are less affected by supernova kicks and so fewer high eccentricity systems are formed. Overall, despite the large differences in the system properties, these three effects in combination leave the detection rates relatively unchanged.

In model \modWRHigh{} we instead \textit{increase} the efficiency of Wolf-Rayet winds by a factor of 5. We note that there is currently no observational support for such a strong increase in the stellar winds of Wolf-Rayet stars, but it is nevertheless still interesting to consider.  In this model the detection rate of BHBHs decreases by over a factor of 10 and BHNSs by over a factor of 2 whilst the NSNS rate is relatively unchanged. Increasing the efficiency of WR winds strongly decreases the final masses of DCOs. This means that many progenitors that would have formed LISA sources under our fiducial assumptions would not have enough mass to produce a DCO, or produce a NS instead of a BH (therefore this effect is stronger on BHBHs than NSNSs). Moreover, DCOs that are formed tend to be less massive and therefore less detectable.

@@

\subsubsection{Effect of Wolf-Rayet winds on mass distribution}

\begin{figure}[tb]
    \centering
    \includegraphics[width=\columnwidth]{fig12_wr_wind_mass_variations.pdf}
    \caption{As Fig.~\ref{fig:lower_mass_gap_variation}, but instead varying Wolf-Rayet wind efficiency (models \modWRLow{} and \modWRHigh{}). The curve for $f_{\rm WR} = 5$ has much higher uncertainties as there are many fewer systems formed in this model (the inverse reasoning also explains the lower uncertainties for $f_{\rm WR} = 0.1$). \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig12_wr_wind_mass_variations.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/variations.ipynb}{\faBook}.}
    \label{fig:wr_wind_mass_variations}
\end{figure}
